Beating Simple Backtracking Search in Subgraph Algorithms\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/026842/1 and EP/M508056/1].}

### 2018-11-25 paper/paper.tex
Nearly there

\begin{abstract}
    The current state of the art in subgraph isomorphism solving involves using degree as a
    value-ordering heuristic to direct backtracking search. Such a search makes a heavy commitment
    to the first branching choice, which is often incorrect. To mitigate this, we introduce and
    evaluate a new approach, which we call ``solution-biased search''. By combining a
    slightly-random value-ordering heuristic, rapid restarts, and nogood recording, we achieve two
    orders of magnitude faster performance on satisfiable instances, whilst not affecting
    performance on unsatisfiable instances. This search can be parallelised in a very simple
    but effective way, giving us a further speedup of over ?? from thirty-six cores, across both
    satisfiable and unsatisfiable instances.  We also show that solution-biased search is also
    suitable for optimisation problems, by using it to improve two maximum common induced subgraph
    algorithms.
\end{abstract}

@@

\begin{figure}[tb]
    \includegraphics*{gen-graph-others.pdf}
    \hfill
    \includegraphics*{gen-graph-others-induced.pdf}

@@

    \includegraphics*{gen-graph-others-zoom.pdf}
    \hfill
    \includegraphics*{gen-graph-others-induced-zoom.pdf}

@@

\begin{figure}[tb]
    \includegraphics*{gen-graph-dds.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-dds.pdf}

@@

\begin{figure}[tb]
    \includegraphics*{gen-graph-value-ordering-heuristics.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-heuristics.pdf}

@@

\begin{figure}[tb]
    \includegraphics*{gen-graph-restarts.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-by-family.pdf}

@@

\begin{figure}[tb]
    \includegraphics*{gen-graph-scatter-biased-goods.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-random.pdf}
    \caption{On the left, not using nogood recording introduces slowdowns, particularly on
    unsatisfiable instances. On the right, using a random value-ordering gives much worse
    performance on many satisfiable instances.}
    \label{figure:features}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics*{gen-graph-parallel.pdf}

@@

    \includegraphics*{gen-graph-scatter-par.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-parconsttick.pdf}

    \caption{Parallel}\label{figure:parallel}
\end{figure}

% \begin{figure}[tb]
%     \includegraphics*{gen-graph-scatter-par-repeat.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-parconsttick-repeat.pdf}
% 
%     \includegraphics*{gen-graph-scatter-parconst-nodes.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-parconsttick-nodes.pdf}
% 
%     \caption{Parallel nodes}\label{figure:parallelnodes}
% \end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics*{gen-graph-mcs.pdf}

@@

    \includegraphics*{gen-graph-scatter-kdown.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-mcsplit.pdf}

>>>>

\begin{abstract}
    The current state of the art in subgraph isomorphism solving involves using degree as a
    value-ordering heuristic to direct backtracking search. Such a search makes a heavy commitment
    to the first branching choice, which is often incorrect. To mitigate this, we introduce and
    evaluate a new approach, which we call ``solution-biased search''. By combining a
    slightly-random value-ordering heuristic, rapid restarts, and nogood recording, we achieve two
    orders of magnitude faster performance on satisfiable instances, whilst not affecting
    performance on unsatisfiable instances. This search can be parallelised in a very simple
    but effective way: across both satisfiable and unsatisfiable instances, we get a further speedup
    of over thirty from thirty-six cores, or one hundred from ten distributed-memory hosts.  We also
    show that solution-biased search is also suitable for optimisation problems, by using it to
    improve two maximum common induced subgraph algorithms.
\end{abstract}

@@

\begin{figure}[tb]
    \includegraphics{gen-graph-others.pdf}
    \hfill
    \includegraphics{gen-graph-others-induced.pdf}

@@

    \includegraphics{gen-graph-others-zoom.pdf}
    \hfill
    \includegraphics{gen-graph-others-induced-zoom.pdf}

@@

\begin{figure}[tb]
    \includegraphics{gen-graph-dds.pdf}
    \hfill
    \includegraphics{gen-graph-scatter-dds.pdf}

@@

\begin{figure}[tb]
    \includegraphics{gen-graph-value-ordering-heuristics.pdf}
    \hfill
    \includegraphics{gen-graph-scatter-heuristics.pdf}

@@

\begin{figure}[tb]
    \includegraphics{gen-graph-restarts.pdf}
    \hfill
    \includegraphics{gen-graph-scatter-by-family.pdf}

@@

\begin{figure}[tb]
    \includegraphics{gen-graph-scatter-biased-goods.pdf}
    \hfill
    \includegraphics{gen-graph-scatter-random.pdf}
    \caption{On the left, not using nogood recording introduces slowdowns, particularly on
    unsatisfiable instances. On the right, using a random value-ordering gives much worse
    performance on many satisfiable instances.}
    \label{figure:features}
\end{figure}

@@

\begin{figure}[tb]
    \includegraphics{gen-graph-parallel.pdf}

@@

    \includegraphics{gen-graph-scatter-par.pdf}
    \hfill
    \includegraphics{gen-graph-scatter-dist.pdf}

    \caption{Above, the cumulative number of instances solved over time, comparing the sequential
    algorithm to results using 32 threads on a single machine, and using five or ten distributed
    memory hosts. Below, instance by instance comparisons.}\label{figure:parallel}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics{gen-graph-mcs.pdf}

@@

    \includegraphics{gen-graph-scatter-kdown.pdf}
    \hfill
    \includegraphics{gen-graph-scatter-mcsplit.pdf}
